---
title: "Exploration of Coastal data"
output:
   bookdown::html_document2:
      toc: true
      toc_float:
         collapsed: false
      toc_depth: 3
      number_sections: true
---

# 2011 LSOA data

We are going to take a look at 2011 data since certain datasets are not yet available for the 2021 census. It is worth noting that the LSOAs do change between census, they may have different names or change shape or new ones ma be created owing to housing developments. The Office for National Statistics (ONS) [open geography portal](https://geoportal.statistics.gov.uk/) is very useful for searching available datasets. For example they do have data tables to map from 2011 LSOAs to 2021 LSOAs.

We obtained 2011 Lower Super Output Areas (LSOA) boundaries from the ONS [here](https://geoportal.statistics.gov.uk/datasets/ons::lsoa-dec-2011-boundaries-generalised-clipped-bgc-ew-v3-2). These are clipped (don't extend into the sea etc) and generalised to 20m (slightly less detail than the actual boundaries). I downloaded these as geojson since this has a lot of tools that can be worked with, and saved them as a file called `lsoa_boundaries_2011.geojson`

This is a `62MB` file and we are only really interested in the coastal towns. And we can start with Dover which we can extract and save like this:

```{r setup, include=FALSE}
# read all of the chunks in here
knitr::opts_chunk$set(echo = TRUE)
knitr::read_chunk("lsoa_extract_dover.R")
knitr::read_chunk("lsoa_merge_ruc.R")
knitr::read_chunk("plot_dover_lsoa.R")
knitr::read_chunk("plot_dover_lsoa_plus_ruc.R")
knitr::read_chunk("bua_extract_dover.R")
knitr::read_chunk("plot_dover_bua.R")
knitr::read_chunk("plot_se_boundary.R")
```

```{r lsoa_extract_dover,eval=F}
```

This then saves the Dover boundaries in `lsoa_boundaries_dover_2011.geojson`. We can then take a look at it using the interactive mapping library `tmap`: 

```{r plot_dover_lsoa,warn=F,message=F}
```

# Rural urban classification

That's more interesting, we could now take the [2011 rural-urban classification data for LSOAs](https://geoportal.statistics.gov.uk/datasets/ons::rural-urban-classification-2011-of-lower-layer-super-output-areas-in-england-and-wales-1/explore) and overlay that. For more information about this classification see [this document](https://www.ons.gov.uk/file?uri=/methodology/geography/geographicalproducts/ruralurbanclassifications/2011ruralurbanclassification/rucoaleafletmay2015tcm77406351.pdf). Assume we have downloaded the data, we can then merge the RUC information with the LSOA boundaries:

```{r lsoa_merge_ruc,eval=F}
```

We can then plot this, note the call to `tmap` is very similar as before, we just use the `RUC11` field to get the correct colour.

```{r plot_dover_lsoa_plus_ruc,warn=F,message=F}
```

# Built up areas

The next thing to look at is the [2011 Built up Areas data](https://geoportal.statistics.gov.uk/datasets/0249dcf56c7d41e5a82bcd89cc37668f/explore).  Built-up Areas (BUAs) and Built-up Area Sub-divisions (BUASDs) are defined as land that is "irreversibly urban in character", including continuous urban development and any areas of intervening open space.


```{r bua_extract_dover,eval=F}
```

And we can then plot this:

```{r plot_dover_bua,warn=F,message=F}
```

# Coastal bounds

```{r plot_se_bounds,warn=F,message=F}
```
